Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-14 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

% Paper title.
\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling a polygonal mesh by
enhancing the object curvature. This method uses an adapted extension
of the Laplace Beltrami operator for hybrid quad/triangle meshes,
to enhance the global curvature. Along with the method, this work
also presents new applications of curvature enhancement in sculpting
and modeling with subdivision surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several modeling techniques have been developed
to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing and creation from sketches \cite{Igarashi1999,Gonen2012},
and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.

Traditional methods for smoothing surfaces from coarse geometry, like
the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
These works generalize the uniform B-cubic splines knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of weights on the vertices to locally control
the zone of influence \cite{Biermann2000}. Instead, the presented
method performs a feature enhancement of the model by parameterizing
the surface curvature and thereby creating a family of different versions
of the same object, preserving therefore the detail of the original
model and a realistic appearance.

On the other hand, many types of brushes have been developed to sculpt
meshes. Brushes that perform inflation end up by losing detail when
inflating the vertices \cite{Stanculescu2011}, in contrast the presented
method allows inflation of the mesh vertices by moving them towards
the opposite curvature direction, conserving the shape and sharp features
of the model.

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
mesh spectrum from what has been presented so far. The method eliminates
the need of preprocessing and allows preservation of the original
topology. Likewise, along with this operator, it is proposed a method
to generate a family of parameterized shapes, in a robust and predictable
way. This method enables customization of the smoothness and curvature,
obtained during the subdivision surfaces process. Finally, it is proposed
a new brush for enhancing silhouette mesh features in modeling and
sculpting.

@@

Many tools have been developed for modeling, based on Laplacian mesh
processing. Thanks to the advantages of the Laplacian operator, these
different tools preserve the surface geometric details when using
them for different processes such as free-form deformation, fusion,
morphing and other application\cite{Sorkine2004}.

Offset polygon mesh methods, based on the curvature defined by the
Laplace Beltrami operator, have been developed. These methods adjust
the shape offset by a constant distance, with high precision as to
minimize the Hausdorf error. Nevertheless, these methods fail to conserve
enough detail because of the smoothing, a crucial issue which depends
on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
representation the computing the offset boundary that are based on
distance field computation, when performing the offset, the topology
of the model may be different from the original, changing the original
design \cite{Chen2011}.

\cite{Gal2009} proposes automatic features detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys with based the first and
second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold. Later the curves are classified by several properties as
planar or non-planar, approximated by lines, circles, ellipses and
other complex shapes. In then the user defines an initial change over
several features and then this change is propagated over other features
with base in the classified shapes and the inter-relationships between
these. This method works fine with objects that have sharp edges composed
of basic geometric shapes such as lines, circles or ellipses but method
has problems to classify when models are smoother with organic forms
because it cannot find the features to edit and preserve.

Digital sculpting can be divided into two principal approaches: based
on polygonal methods and voxel grid-based methods. Brushes for inflate
operations in polygonal methods only depends on the normal at each
vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
allow to add or remove voxels, for produce polygonal meshes require
processing isosurfaces from volume \cite{Galyean1991}. The problem
whit this type of operations is the difficult to maintain surface
details during larger scale deformation.

@@

Computer graphics objects which have been reconstructed from real
world, contain undesirable noise. Laplacian Smooth techniques allow
noise reduction on a mesh's surface with minimal changes on its shape
while still preserves desirable geometry as well as the shape of the
original model.

The functional used in many Laplacian smoothing approaches to constrain
energy minimization is based on a total curvature of a surface $S$.

@@

\caption{\label{fig:voronoi_region}Area of Voronoi region around $v_{i}$
in dark blue.\protect \\
 $v_{j}$ 1-ring neighbors around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$
opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
\end{figure}

Consider a surface $S$ composed by a set of triangles around vertex
$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The change in the area produced
by the movement of $v_{i}$ is named gradient of \textit{Voronoi region
\cite{Pinkall1993,Desbrun1999,Meyer2003}.}

@@

If we normalize this gradient in equation (\ref{eq:eq_gradient_voronoi_area})
by the total area in 1-ring around $v_{i}$, we have the \textit{discrete
mean curvature normal} of a surface $S$ as shown in equation (\ref{eq:discrete_mean_curvature_normal}).

@@

The \textit{Laplace Beltrami operator} LBO denoted $\triangle_{g}$
is used for measures mean curvature normal of the Surface $S$ \cite{Pinkall1993}.

@@

The LBO has desirable features: one feature of the LBO is in direction
of surface area minimization, allowing to minimize energy using it
on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

Our method allows the editing of geometric features using the curvature
enhancement and smoothing, generating a parameterized family of shapes
from a set of vertices which represent a coarse sketch of the desired
model. Our approach can be mixed with traditional or uniform subdivision
surfaces methods, is iterative and converges towards a continuous
and smooth version of the original model.

Unlike other methods, our method allows to use mixed arbitrary types
of mesh representation as triangles and quads, exploiting the basic
geometrical relationships facilitating and ensuring convergence of
the algorithm and similar shapes consistent with the original shape
against the other methods.

@@

Livingstone elephant model is provided courtesy of INRIA and ISTI
by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
Commons Attribution 3.0 Unported License. Dinosaur model is under
public domain, courtesy of Blender Foundation.

>>>>

% Paper title.
\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhanced shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for constructing a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses an
adapted extension of the Laplace Beltrami operator, resulting in a large variety of meshes. Along with the
method, this work presents new applications in sculpting and
modeling, with subdivision of surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Nevertheless,
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, which is used to maintain realistic shapes, creating a family of different versions of the same
object and therefore preserving the detail of the original model and
a realistic appearance. Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}. Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}. It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles. The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}. In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a
larger mesh spectrum from what has been presented so far. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Likewise, along with this operator, it is proposed
a method to generate a family of parameterized shapes, in a robust
and predictable way. This method enables customization of the smoothness
and curvature, obtained during the subdivision surfaces process. Finally,
it is proposed a new brush for enhancing the silhouette mesh features
in modeling and sculpting.

@@

Many tools have been developed for modeling, based on the Laplacian
mesh processing. Thanks to the advantages of the Laplacian operator,
these different tools preserve the surface geometric details when
using them for different processes such as free-form deformation,
fusion, morphing and other application\cite{Sorkine2004}.

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with enough precision
as to minimize the Hausdorff error. Nevertheless, these methods fail
to conserve sufficient detail because of the smoothing, a crucial
issue which depends on the offset size \cite{Zhuo2012}. In volumetric
approaches, in case of point-based representations, the offset boundary
computation is based on the distance field and therefore when calculating
such offset, the topology of the model may be different to the original
\cite{Chen2011}.

Gai et al. \cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold. Likewise, curves have been also classified as planar or
non-planar, approximated by lines, circles, ellipses and other complex
shapes. In such case, the user defines an initial change over several
features which is propagated towards other features, based
on the classified shapes and the inter-relationships between them.
This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since
it cannot find the proper features to edit.

Digital sculpting have been traditionally approached either under
a polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing of
isosurfaces from a volume \cite{Galyean1991}. The drawback comes from the difficulty of maintaining the surface details
during larger scale deformations.

@@

Computer objects, reconstructed from the real
world, are usually noisy. Laplacian Smooth techniques allow a proper
noise reduction on the mesh surface with minimal shape changes,
while still preserving a desirable geometry as well as the original shape.

Many smoothing Laplacian functionals regularize the surface energy by controling the total surface curvature $S$.

@@

\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
in dark blue.\protect \\
 $v_{j}$ belong to the first neighborhood around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$ are the
opposite angles to the edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
\end{figure}

Consider a surface $S$, composed of a set of triangles, around the vertex
$v_{i}$. Let us define the \textit{Voronoi region} of $v_{i}$, as
show in figure \ref{fig:voronoi_region}, The area change produced
by the movement of $v_{i}$ is called the gradient of the \textit{Voronoi region
\cite{Pinkall1993,Desbrun1999,Meyer2003}.}

@@

If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is normalized 
by the total area of the first neighborhood around $v_{i}$, the \textit{discrete
mean curvature normal} of a surface $S$  is obtained, as shown in equation (\ref{eq:discrete_mean_curvature_normal}).

@@

The \textit{Laplace Beltrami operator} LBO, noted as $\triangle_{g}$,
is used for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.

@@

The LBO has desirable properties: the LBO points out to the direction
of the minimal surface area, minimizing the energy of the total surface curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

The method allows edition of geometric features using the curvature
enhancement and smoothing, generating a parameterized family of shapes
from a set of vertices which represent a coarse sketch of the desired
model. Our approach can be mixed with traditional or uniform subdivision
surfaces methods, is iterative and converges towards a continuous
and smooth version of the original model.

@@

Livingstone elephant model is provided courtesy of INRIA and ISTI
by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
are under public domain, courtesy of Blender Foundation.
